
---
title: "Documentation"
author: "Pawel Pienczuk"
date: "2025-05-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Documentation for what_to_buy()

This function downloads stock data from the Warsaw Stock Exchange and plots closing prices.

## Requirements
- `lubridate`
- `ggplot2`
- `tidyr`

## Example

```{r eval=FALSE}
source("https://raw.githubusercontent.com/m-dadej/Downloading-and-aggregating-stocks/master/getWSE.R")

what_to_buy <- function(wektor, from, to){
  stopifnot(
    is.character(wektor),
    is.character(from), !is.na(lubridate::ymd(from)),
    is.character(to), !is.na(lubridate::ymd(to))
  )

  df <- getWSE(
    tickers = wektor,
    ohlcv = "Close",
    from = from,
    to = to,
    freq = "daily",
    corpo_action = c("div", "split")
  )

  p <- ggplot2::ggplot()
  x_col <- df[[1]]
  x_label <- names(df)[1]

  for (i in 2:ncol(df)) {
    seria_df <- data.frame(
      x = x_col,
      y = df[[i]],
      seria = names(df)[i]
    )
    p <- p + ggplot2::geom_line(data = seria_df, ggplot2::aes(x = x, y = y, color = seria))
  }

  p <- p + ggplot2::labs(x = x_label, y = "Wartość", color = "Seria") +
    ggplot2::theme_minimal()
  return(list(df, p))
}
```

## Usage
```{r what_to_buy_example, message=FALSE, warning=FALSE}
shares_to_consider <- c("xtb", "pko", "dbc")
startdate <- "2022-02-01"
enddate <- "2024-12-13"

output <- what_to_buy(shares_to_consider, startdate, enddate)

#Display the plot:
print("Shares values:")
plot <- output[[2]]
plot

#Display the data frame with values for each day:
sharesdata <- output[[1]]
knitr::kable(head(sharesdata), caption = "Shares data for further analysis:")

```


## Output

The function returns a list with:
1. A data frame (`df`) of the downloaded closing prices.
2. A ggplot object (`p`) showing the trends for each ticker.

### Disclaimer

This function relies on the external `getWSE()` script by m-dadej, available on GitHub. You can find the source script here: [getWSE.R on GitHub](https://github.com/m-dadej/Downloading-and-aggregating-stocks/blob/master/getWSE.R). The data includes corporate actions.

## Function 2: `parts_distribution()`

This function calculates and visualizes the distribution of part variants within a manufacturing batch, considering a missing rate.

### Usage

Provide the number of part types, the total batch size, and the expected missing rate.


```{r parts_distribution_example, message=FALSE, warning=FALSE}
# --- Include the function definition here for a self-contained Rmd example ---
# (In a real package, this would not be necessary as the function would be loaded)

# Define parameters
num_parts <- 15
batch_size <- 800
missing_rate_val <- 1.1

# Call the function
parts_results <- parts_distribution(no_parts = num_parts, batch = batch_size, missing_rate = missing_rate_val)

# Display the resulting plot
print("Parts Distribution Plot:")
parts_results$plot

# Display the resulting data frame
print("Parts Distribution Data:")
knitr::kable(parts_results$data_frame)

# Display the sum in batch
print(paste("Total parts in technological distribution:", parts_results$sum_in_batch))
```

## Function 3: `analyze_parts_distribution()`

This function takes the output from `parts_distribution()` and performs further analysis, including descriptive statistics, normality checks, and fitting a normal distribution curve to the technological data plot.

### Usage

Pass the list output from `parts_distribution()` to this function.

```{r analyze_parts_distribution_example, message=FALSE, warning=FALSE}
# --- Include the function definition here for a self-contained Rmd example ---
# (In a real package, this would not be necessary as the function would be loaded)

# Assuming parts_results from the previous chunk is available
# If running this chunk independently, you would need to run parts_distribution first:
# num_parts <- 15
# batch_size <- 800
# missing_rate_val <- 1.1
# parts_results <- parts_distribution(no_parts = num_parts, batch = batch_size, missing_rate = missing_rate_val)


# Call the analysis function
analysis_results <- analyze_parts_distribution(parts_results)

# Display the summary statistics table
print("Summary Statistics:")
knitr::kable(analysis_results$summary_stats)

# Display the normality analysis table
print("Normality Analysis:")
knitr::kable(analysis_results$normality_analysis)

# Display the technological probabilities table
print("Technological Probabilities:")
knitr::kable(analysis_results$technological_probabilities)

# Display the modified plot with normal fit
print("Parts Distribution Plot with Normal Fit:")
analysis_results$plot_with_normal_fit
```
